An Efficient Interpolation Technique for Jump Proposals in Reversible-Jump Markov Chain Monte Carlo Calculations

### 2011-03-17 paper.tex
Corrected grants for WMF.
Fixed WMF affiliation.

\affiliation{Northwestern University Center for Interdisciplinary
  Research and Education in Astrophysics}

@@

We are grateful to Neil Cornish for interesting discussions.  IM
acknowledges support from the NSF Astronomy and Astrophysics
Postdoctoral Fellowship, award AST-0901985.  WF acknowledges support
from NSF grants CAREER AST-0449558 and AST0908930.

>>>>

\affiliation{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA) \\ Department of Physics and Astronomy, Northwestern University}

@@

We are grateful to Neil Cornish for interesting discussions.  IM
acknowledges support from the NSF Astronomy and Astrophysics
Postdoctoral Fellowship, award AST-0901985.  WF acknowledges support
from NSF grant AST0908930 and NASA grant NNX09AJ56G.
